Goal Recognition as Planning with Unknown Domain Models

### 2019-02-07 doc/ijcai-19-goalRecognition/goalRecognition.tex
example extended for ijai19 paper on goal recognition

\begin{figure}[hbt!]
	{\scriptsize\tt
		{\bf 00} : (insert\_pre\_stack\_holding\_v1) \\
		01 : (insert\_pre\_stack\_clear\_v2)\\
		{\bf 02} : (insert\_eff\_stack\_clear\_v1)\\
		03 : (insert\_eff\_stack\_clear\_v2)\\
		04 : (insert\_eff\_stack\_handempty)\\
		05 : (insert\_eff\_stack\_holding\_v1)\\
		06 : (insert\_eff\_stack\_on\_v1\_v2)\\
		{\bf 07} : (apply\_stack blockA blockB)\\
	}
	\caption{\small Plan computed when solving the classical planning problem output by our compilation corresponding to a classical planning with unknown domain models.}
	\label{fig:plan-lplan}
\end{figure}

Figure~\ref{fig:plan-lplan} shows a solution plan computed when solving a $P'=\tup{F',A',I,G}$ classical planning problem output by our compilation. In the initial state of that problem the robot is holding {\tt blockA} while {\tt blockB} is clear and the single problem goal is having {\tt blockA} on top of {\tt blockB}. The plan shows that the {\em insert} actions for the action model {\tt\small stack} (steps $00-01$ insert the preconditions of the {\tt\small stack} model, steps $02-06$ insert the action model effects), and step $07$ is the plan postfix that applies the programmed action model to achieve the goals $G$. Note that another valid solution could be computed for instance, inserting the same preconditions and effects into the {\em unstack} action model and then applying the {\tt\small (unstack blockA blockB)} action instead of {\tt\small(stack blockA blockB)}.

>>>>

\begin{figure}[hbt!]
	{\tiny\tt

\begin{tabular}{ll}
		{\bf 00}:(insert\_pre\_stack\_holding\_v1) & 09:(insert\_pre\_pickup\_handempty)\\
		01:(insert\_pre\_stack\_clear\_v2) & {\bf 10}:(insert\_eff\_pickup\_clear\_v1)\\
		{\bf 02}:(insert\_eff\_stack\_clear\_v1) & 11:(insert\_eff\_pickup\_ontable\_v1)\\
		03:(insert\_eff\_stack\_clear\_v2) & 12:(insert\_eff\_pickup\_handempty)\\
		04:(insert\_eff\_stack\_handempty) & 13:(insert\_eff\_pickup\_holding\_v1)\\
		05:(insert\_eff\_stack\_holding\_v1) & {\bf 14}:(apply\_pickup blockB)\\
		06:(insert\_eff\_stack\_on\_v1\_v2) & 15:(apply\_stack blockB blockC)\\
		{\bf 07}:(insert\_pre\_pickup\_clear\_v1) & 16:(apply\_pickup blockA)\\
		08:(insert\_pre\_pickup\_ontable\_v1) & 17:(apply\_stack blockA blockB)\\             
\end{tabular}
}
	\caption{\small Plan computed when solving the classical planning problem output by our compilation corresponding to a classical planning with unknown domain models.}
	\label{fig:plan-lplan}
\end{figure}

Figure~\ref{fig:plan-lplan} shows a solution plan computed when solving a $P'=\tup{F',A',I,G}$ classical planning problem output by our compilation. In the initial state of that problem three  blocks (namely {\small\tt blockA},{\small\tt blockB} and {\small\tt blockC}) are clear and on top of the table and the robot hand is empty. The problem goals is having the 3-block tower {\tt blockA} on top of {\tt blockB} and {\tt blockB} on top of {\tt blockC}. The plan shows that the {\em insert} actions for the action model {\tt\small stack} (steps $00-01$ insert the preconditions of the {\tt\small stack} model, steps $02-06$ insert the action model effects), steps $07-13$ insert the preconditions and effects of the {\tt\small pickup} action model and finally, steps $14-17$ is the plan postfix that applies the programmed action model to achieve the goals $G$. Note that another valid solution could be computed for instance, inserting the same preconditions and effects into the {\em putdown} and {\em unstack} action models and then applying instead the four step postfix {\tt\small (putdown blockB), (unstack blockB blockC), (putdown blockA), (unstack blockA blockB)}.
